\ttitle

### 2016-03-26 Chapters/CRP_Complications.tex
CRP_Complications
- Remove other mentions of albumin, wcc or neutrophil counts

Patients had routine measurements of inflammatory markers including C-reactive protein (CRP) and differential white cell counts from the day before surgery and every day for at least a week after surgery. 
These results were collected from the hospital laboratory database using an automated MS Access application as outlined in Appendix \ref{AppendixAccessDatabase}.

@@

However, there is no useful clinical application for the association between CRP in the early postoperative period and  pancreatic fistula as the diagnosis of POPF is based on the amylase content in surgical drains on the third postoperative day. 
Moreover, early postoperative CRP did not predict the severity of the pancreatic fistula either.

@@

The difference in white cell count and neutrophil count was not clinically significant between patients who did or did not have an infective complication. 
This finding is similar to one of the earliest reports on the role of serial CRP measurements in predicting septic complications after surgery \parencite{mustard_c-reactive_1987} as well as in several subsequent reports \parencite{matthiessen_increase_2008, welsch_persisting_2008, dutta_persistent_2011}. 
The temporal association between CRP and infective complications may reflect the sensitivity of CRP as a marker of systemic inflammation. 
This study was not designed to look at inflammatory markers later in the postoperative period. 
However, Mustard and co-workers monitored CRP, white cell count and temperature for 14 days after surgery and found that CRP was the only reliable marker of septic complications \parencite{mustard_c-reactive_1987}.

>>>>

Patients had routine measurements of inflammatory markers including C-reactive protein (CRP) from the day before surgery and every day for at least a week after surgery. 
These results were collected from the hospital laboratory database using an automated MS Access application as outlined in Appendix \ref{AppendixAccessDatabase}.

@@

However, there is no useful clinical application for the association between CRP in the early postoperative period and  pancreatic fistula as the diagnosis of POPF is based on the amylase content in surgical drains on the third postoperative day. 
Moreover, early postoperative CRP did not predict the severity of the pancreatic fistula.

@@

The temporal association between CRP and infective complications may reflect the sensitivity of CRP as a marker of systemic inflammation. 
This finding is similar to one of the earliest reports on the role of serial CRP measurements in predicting septic complications after surgery \parencite{mustard_c-reactive_1987} as well as in several subsequent reports \parencite{matthiessen_increase_2008, welsch_persisting_2008, dutta_persistent_2011}. 
This study was not designed to look at inflammatory markers later in the postoperative period. 
However, Mustard and co-workers monitored CRP, white cell count and temperature for 14 days after surgery and found that CRP was the only reliable marker of septic complications \parencite{mustard_c-reactive_1987}.
